### 2017-01-13 Projects/DelCo_2014_2015/Reports/Propane_Gas_Fire_Experiments/TeX_Files/Propane_Gas_Fire_Experiments.tex
DelCo report: Add header info to longtables.
Minor change to gas burner report

\subsubsection{First Floor of Both Structures}
The first floor of each structure had outer walls composed of interlocking concrete blocks with equal side lengths of 0.61~m (2~ft). The joints and gaps between the blocks were filled with high temperature insulation. All doors along the outer walls were composed of steel.

@@

Dimensioned floor plans of the East and West Structures are presented in Figures~\ref{fig:east_dimensioned_plan}~and~\ref{fig:west_dimensioned_plan}, respectively.

@@

\caption{East Structure Channel List\label{table:east_channel_list}} \\

@@

\caption{West Structure Channel List\label{table:west_channel_list}} \\

>>>>

\subsubsection{First Floor of Both Structures}
The first floor of each structure had outer walls composed of interlocking concrete blocks measuring 0.6~m (2.0~ft) wide, 0.6~m (2.0~ft) high, and 1.2~m (4.0~ft) long. The joints and gaps between the blocks were filled with high temperature insulation. All doors along the outer walls were composed of steel.

@@

Dimensioned floor plans of the East and West Structures are presented in Figs.~\ref{fig:east_dimensioned_plan}~and~\ref{fig:west_dimensioned_plan}, respectively.

@@

\caption[East Structure Channel List]{East Structure Channel List}
\label{table:east_channel_list}\\
\endfirsthead
\caption[]{East Structure Channel List (continued)} \\

@@

\caption[West Structure Channel List]{West Structure Channel List}
\label{table:west_channel_list}\\
\endfirsthead
\caption[]{West Structure Channel List (continued)} \\
